Aa Language Reference Manual

### 2022-07-10 v2/Ahir-asm/devel/docs/AaLRM.tex
RtlThread generated VHDL sometimes infers a spurious latch. Removed.

Pipe variable declarations can also be appended by
the following keywords:
\begin{verbatim}
   ($in | $out)? ($signal)? 
\end{verbatim}
These additional keywords mean the following things:
\begin{itemize}
\item Inclusion of ``\$in'' (respectively ``\$out'') means
that the pipe is a read-only (respectively write-only) object.
\item The ``\$signal'' keyword means that the pipe behaves
like a variable.  That is, it remembers the last value
that was written to it\footnote{    
Note that a read from a signal will block until the
signal has been written into at least once!}.
\end{itemize}
Pipe depths can be specified by parameters or parameter
expressions.
\item {\bf Constant} variables declared at
the program scope are globally visible and have
initial values which can never be altered in the program.
Thus, an assignment to a constant is an error.
A constant declaration has the form
\begin{verbatim}
$constant <constant-name>: <constant-type> := <initial-value>
\end{verbatim}
For example
\begin{verbatim}
$constant wordlength: $uint<32> := 16
\end{verbatim}
\item {\bf Implicit} or {\bf Static Single Assignment}
variables are created by statements in the \Aa program
(as described below in Section \ref{sec:Statements}).
These are analogous to registers that can be written
into only from one point,  but can be
read from several points in the program.
Implicit variables are not declared, but are defined
by the statements which write to them.
\end{itemize}

@@

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Useful Unary logical expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\end{itemize}

@@

>>>>

Pipe variable declarations can also be appended by
the following keywords:
\begin{verbatim}
   ($in | $out)? ($signal)? 
\end{verbatim}
These additional keywords mean the following things:
\begin{itemize}
\item Inclusion of ``\$in'' (respectively ``\$out'') means
that the pipe is a read-only (respectively write-only) object.
\item The ``\$signal'' keyword means that the pipe behaves
like a variable.  That is, it remembers the last value
that was written to it\footnote{Note that the signal is initialized to 0.}.
\end{itemize}
Pipe depths can be specified by parameters or parameter
expressions.
\item {\bf Constant} variables declared at
the program scope are globally visible and have
initial values which can never be altered in the program.
Thus, an assignment to a constant is an error.
A constant declaration has the form
\begin{verbatim}
$constant <constant-name>: <constant-type> := <initial-value>
\end{verbatim}
For example
\begin{verbatim}
$constant wordlength: $uint<32> := 16
\end{verbatim}
\item {\bf Implicit} or {\bf Static Single Assignment}
variables are created by statements in the \Aa program
(as described below in Section \ref{sec:Statements}).
These are analogous to registers that can be written
into only from one point,  but can be
read from several points in the program.
Implicit variables are not declared, but are defined
by the statements which write to them.
\end{itemize}

@@

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Useful Unary logical expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\item Zero, One expressions.
\end{itemize}

@@

\subsection{Zero, One expressions}

For convenience, the following expressions represent
a zero and one value with the specified uint type:
\begin{verbatim}
$zero<width>
$one<width>
\end{verbatim}

The following expression 
\begin{verbatim}
$zero<16>
\end{verbatim}
expands to
\begin{verbatim}
($bitcast ($uint<16>) 0)
\end{verbatim}
and the  following expression
\begin{verbatim}
$one<16>
\end{verbatim}
expands to
\begin{verbatim}
($bitcast ($uint<16>) 1)
\end{verbatim}
